---
title: "Homework Assignment: Sentiment Analysis of Emma"
format: html
editor: visual
author: Sam Feinberg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.align  = "center",
                      fig.height = 3, fig.width = 4)
ggplot2::theme_set(ggplot2::theme_bw() + ggplot2::theme(strip.background = ggplot2::element_rect(fill = "white")))
```

**Title**: Exploring Joyful Language in Jane Austen’s *Emma* using Tidytext

### **Instructions**

Complete the following exercises using the appropriate packages in R. Ensure that your solutions are optimized and use functional programming principles where applicable.

1.  Load the necessary libraries.
2.  Answer each question in separate R code chunks.
3.  Provide detailed explanations for your approach.
4.  Submit the rendered HTML file.

#### **Objective**:

Use the **`tidytext`** package and three different **sentiment lexicons** (`nrc`, `afinn`, `bing`) to explore **positive/joyful words** in *Emma* by Jane Austen. You will tokenize the text, apply sentiment filters, visualize frequent sentiment words using `ggplot2`, and create a word cloud.

### **Tasks**:

1.  **Data Preparation**

    -   Load the `austen_books()` dataset from the **`janeaustenr`** package.
    -   Group by book and detect chapter boundaries using regex.
    -   Create `linenumber` and `chapter` columns.

```{r}
#| label: Part 1
#| warning: false

library(tidyverse)
library(tidytext)
library(janeaustenr)
library(dplyr)
library(textdata)
library(stringr)

austen_books() |>
  distinct(book)

austen_books_chapt_and_line <- austen_books() |>
  group_by(book) |>
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text,
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) |>
  ungroup()

head(austen_books_chapt_and_line, n = 20)

# In this part, I first loaded pacakges to use. I then loaded this austen_books() datasets, and used distinct to see all the books in the dataset. I then grouped by book and used mutate() from dplyr to create rows for line number and chaper. To tell where chapters started, I used regex.

```

1.  **Tokenization**

    -   Use `unnest_tokens()` to tokenize text into individual words.

```{r}
#| label: Part 2

austen_tokenized <- austen_books_chapt_and_line |>
  unnest_tokens(word, text) 

head(austen_tokenized, n = 10)

# In this part, I used unnest_tokens() to tokenize the text from austen_books_chapt_and_line by word, and I saved it as a tibble.

```

1.  **Sentiment Analysis**

    -   Filter joy/positive words from **each** of the three sentiment lexicons:

        -   `nrc` (joy)
        -   `afinn` (positive scores ≥ 1)
        -   `bing` (positive)

    -   Join each with *Emma*'s text and:

        -   Count word frequency.
        -   Filter for frequently occurring words (`n > 50`).
        -   Visualize using a **bar chart** (`ggplot2`) and a **word cloud** (`wordcloud`).

2.  **Push to GitHub**

    -   Push your complete rendred qmd (`.html` file) to a **GitHub repository**.

    -   Your file should include:

        -   Data wrangling
        -   Sentiment filtering and joins
        -   Visualization code

    -   You must include **at least 5 meaningful commits** to document your workflow.

------------------------------------------------------------------------

## **Rubric 100 Points**

| Category                                       | Points  |
|------------------------------------------------|---------|
| Step 1: Data wrangling (linenumber, chapter)   | 10      |
| Step 2: Tokenization                           | 10      |
| Step 3a: NRC sentiment analysis + plots        | 10      |
| Step 3b: AFINN sentiment analysis + plots      | 10      |
| Step 3c: BING sentiment analysis + plots       | 10      |
| Code readability, structure, and comments      | 10      |
| Word cloud for each lexicon                    | 20      |
| GitHub submission                              |         |
| Commit history (at least 5 meaningful commits) | 20      |
| **Total**                                      | **100** |

Good Luck!
